---
title: "Mitigation measures"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(writexl)
library(readxl)
```

The DPMFA model needs to be run using different setup files in order to get output for a baseline and all the different scenario's that include mitigation measures we want to study. Those output data should then be combined into 1 dataframe which is further analysed here

```{r data using mean}

# MIT_data_combined |> distinct(Measure) |> print(n=25)
data_folder <- "/rivm/r/E121554 LEON-T/03 - uitvoering WP3/DPMFA_output"
load(paste0(data_folder,"/Mitigation_data_combined_v1_20240526.Rdata"))

MIT_data_combined <- 
  MIT_data_combined |> 
  filter(!is.na(Measure)) # only neede because Mitigation measure 2 file had domestic and import pellets

MIT_data_combS <-
  MIT_data_combined |> 
  ungroup() |> 
  group_by(Type,
           Scale,
           Material_Type,
           Year,
           Source,
           MIT_Source,
           Measure) |> 
  summarise(Measure_t = sum(Mean_mass_t)) |> 
  ungroup()



# MIT_data_combined |> group_by_all() |> 
#   filter(n()>1) |> ungroup() # able to check for duplicate rows

Baseline1 <- 
  MIT_data_combS |> 
  filter(Measure == 0) |> 
  mutate(BaselinePerSMITCombo_t = Measure_t, .keep = "unused" ) |> 
  select(-Measure)


Baseline2 <- 
  Baseline1 |> 
  ungroup() |> 
  group_by(Type,
           Scale,
           Material_Type,
           MIT_Source,
           Year) |> 
  summarise(BaselinePerSMITCombo_t = sum(BaselinePerSMITCombo_t)) |> 
  filter(Material_Type != "macro") |> 
  bind_rows(
    Baseline1 |>
      filter(Material_Type == "macro") |> 
      ungroup() |> 
      group_by(Year,Scale,Type, Material_Type) |> 
      summarise(BaselinePerSMITCombo_t = sum(BaselinePerSMITCombo_t),
                MIT_Source         = "Macropalstics"))

Baseline3 <-
  Baseline1 |> 
  ungroup() |> 
  group_by(Type,
           Scale,
           Material_Type,
           Year) |> 
  summarise(BaselineTotMicroMacro_t = sum(BaselinePerSMITCombo_t))


Baseline <- 
  Baseline1 |> 
  left_join(Baseline2) |>
  left_join(Baseline3)

MIT_data_combS <-
  MIT_data_combS |> 
  filter(Measure != 0) |> 
  left_join(Baseline, by = c(
    "Type",
    "Scale",
    "Material_Type",            
    "Year",
    "MIT_Source",
    "Source"
  ))


MIT_data_combS2 <- 
  MIT_data_combS |> 
  mutate(Reduction_t = BaselinePerSMITCombo_t-Measure_t)

# Load the combinations
data_folder2 <- "/rivm/r/E121554 LEON-T/03 - uitvoering WP3/DPMFA_output/Mitigation_data/"
msd <- read_excel(path = paste0(data_folder2, "Measure_descriptions.xlsx")) |> 
  filter(Measure != "Baseline") |> 
  mutate_at(c("Measure","GenRed"),as.numeric)



MeasureReduction <- # get the reduction summed per measure for comparison with total plastics emitted
  MIT_data_combS2 |> 
  left_join(msd, by = "Measure") |> 
  ungroup() |> 
  group_by(Measure,
           Material_Type ,
           Year,
           GenRed,
           Description) |> 
  summarise(ReductionMtot_t = sum(Reduction_t)) |> 
  full_join(Baseline3) |> 
  mutate(Effectifity = ((ReductionMtot_t)/BaselineTotMicroMacro_t)/GenRed,
         FracReduc = ((ReductionMtot_t)/BaselineTotMicroMacro_t))



MeasureMITComboReduction <- # get the reduction summed per measure for comparison with total plastics emitted
  MIT_data_combS2 |> 
  left_join(msd, by = "Measure") |> 
  ungroup() |> 
  group_by(Measure,
           RelevantSource,
           Material_Type ,
           Year,
           GenRed,
           Description) |> 
  summarise(ReductionMMIT_t = sum(Reduction_t)) |> 
  filter(Material_Type != "macro") |> 
  bind_rows(
    MIT_data_combS2 |>
      left_join(msd, by = "Measure") |> 
      filter(Material_Type == "macro") |> 
      ungroup() |> 
      group_by(Year, RelevantSource,Measure,
               GenRed,Description, Material_Type) |> 
      summarise(ReductionMMIT_t = sum(Reduction_t),
                RelevantSource         = "Macropalstics") ) |> 
  left_join(Baseline2 |> ungroup() |> 
              mutate(RelevantSource = MIT_Source) |> 
              select(-MIT_Source)) |> 
  mutate(Effectifity = (BaselinePerSMITCombo_t /BaselinePerSMITCombo_t )/GenRed,
         FracReduc = (BaselinePerSMITCombo_t /BaselinePerSMITCombo_t ))


write.xlsx(list(MeasureMITComboReduction, MeasureReduction),                     
           file = paste0(data_folder,"/Output_tables/Mitigation_Measure_effect.xlsx"))


```


```{r data using p50}

# MIT_data_combined |> distinct(Measure) |> print(n=25)
# data_folder <- "/rivm/r/E121554 LEON-T/03 - uitvoering WP3/DPMFA_output"
# load(paste0(data_folder,"/Mitigation_data_combined_v1_20240526.Rdata"))

MIT_data_combined<- MIT_data_combined_p50

MIT_data_combined <- 
  MIT_data_combined |> 
  filter(!is.na(Measure)) # only neede because Mitigation measure 2 file had domestic and import pellets

MIT_data_combS <-
  MIT_data_combined |> 
  ungroup() |> 
  group_by(Type,
           Scale,
           Material_Type,
           Year,
           Source,
           MIT_Source,
           Measure) |> 
  summarise(Measure_t = sum(P50_mass_t)) |> 
  ungroup()



# MIT_data_combined |> group_by_all() |> 
#   filter(n()>1) |> ungroup() # able to check for duplicate rows

Baseline1 <- 
  MIT_data_combS |> 
  filter(Measure == 0) |> 
  mutate(BaselinePerSMITCombo_t = Measure_t, .keep = "unused" ) |> 
  select(-Measure)


Baseline2 <- 
  Baseline1 |> 
  ungroup() |> 
  group_by(Type,
           Scale,
           Material_Type,
           MIT_Source,
           Year) |> 
  summarise(BaselinePerSMITCombo_t = sum(BaselinePerSMITCombo_t)) |> 
  filter(Material_Type != "macro") |> 
  bind_rows(
    Baseline1 |>
      filter(Material_Type == "macro") |> 
      ungroup() |> 
      group_by(Year,Scale,Type, Material_Type) |> 
      summarise(BaselinePerSMITCombo_t = sum(BaselinePerSMITCombo_t),
                MIT_Source         = "Macropalstics"))

Baseline3 <-
  Baseline1 |> 
  ungroup() |> 
  group_by(Type,
           Scale,
           Material_Type,
           Year) |> 
  summarise(BaselineTotMicroMacro_t = sum(BaselinePerSMITCombo_t))

Baseline4 <-
  Baseline1 |> 
  ungroup() |> 
  group_by(Type,
           Scale,
           Year) |> 
  summarise(BaselineTot_t = sum(BaselinePerSMITCombo_t))

Baseline <- 
  Baseline1 |> 
  left_join(Baseline2) |>
  left_join(Baseline3) |> 
  left_join(Baseline4)

MIT_data_combS <-
  MIT_data_combS |> 
  filter(Measure != 0) |> 
  left_join(Baseline, by = c(
    "Type",
    "Scale",
    "Material_Type",            
    "Year",
    "MIT_Source",
    "Source"
  ))


MIT_data_combS2 <- 
  MIT_data_combS |> 
  mutate(Reduction_t = BaselinePerSMITCombo_t-Measure_t)

# Load the combinations
data_folder2 <- "/rivm/r/E121554 LEON-T/03 - uitvoering WP3/DPMFA_output/Mitigation_data/"
msd <- read_excel(path = paste0(data_folder2, "Measure_descriptions.xlsx")) |> 
  filter(Measure != "Baseline") |> 
  mutate_at(c("Measure","GenRed"),as.numeric)



MeasureReductionMM <- # get the reduction summed per measure for comparison with total plastics emitted
  MIT_data_combS2 |> 
  left_join(msd, by = "Measure") |> 
  ungroup() |> 
  group_by(Measure,
           Material_Type ,
           Year,
           GenRed,
           Description) |> 
  summarise(ReductionMtot_t = sum(Reduction_t)) |> 
  full_join(Baseline3) |> 
  full_join(Baseline4) |> 
  mutate(EffectifityMM = ((ReductionMtot_t)/BaselineTotMicroMacro_t)/GenRed,
         FracReducMM = ((ReductionMtot_t)/BaselineTotMicroMacro_t))


MeasureReductionTot <- # get the reduction summed per measure for comparison with total plastics emitted
  MIT_data_combS2 |> 
  left_join(msd, by = "Measure") |> 
  ungroup() |> 
  group_by(Measure,
           Year,
           GenRed,
           Description) |> 
  summarise(ReductionMtot_t = sum(Reduction_t)) |> 
  # full_join(Baseline3) |> 
  full_join(Baseline4) |> 
  mutate(EffectifityMM = ((ReductionMtot_t)/BaselineTot_t)/GenRed,
         FracReducTot = ((ReductionMtot_t)/BaselineTot_t))


MeasureMITComboReduction <- # get the reduction summed per measure for comparison with total plastics emitted
  MIT_data_combS2 |> 
  left_join(msd, by = "Measure") |> 
  ungroup() |> 
  group_by(Measure,
           RelevantSource,
           Material_Type ,
           Year,
           GenRed,
           Description) |> 
  summarise(ReductionMMIT_t = sum(Reduction_t)) |> 
  filter(Material_Type != "macro") |> 
  bind_rows(
    MIT_data_combS2 |>
      left_join(msd, by = "Measure") |> 
      filter(Material_Type == "macro") |> 
      ungroup() |> 
      group_by(Year, RelevantSource,Measure,
               GenRed,Description, Material_Type) |> 
      summarise(ReductionMMIT_t = sum(Reduction_t),
                RelevantSource         = "Macropalstics") ) |> 
  left_join(Baseline2 |> ungroup() |> 
              mutate(RelevantSource = MIT_Source) |> 
              select(-MIT_Source)) |> 
  mutate(Effectifity = (ReductionMMIT_t /BaselinePerSMITCombo_t )/GenRed,
         FracReduc = (ReductionMMIT_t /BaselinePerSMITCombo_t ))


write.xlsx(list(MeasureMITComboReduction, MeasureReductionMM,MeasureReductionTot),
           file = paste0(data_folder,"/Output_tables/Mitigation_Measure_effect_p50.xlsx"))


```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
